hbm_paper_results

### 2024-02-02 paper_lbcc_results.Rmd
running lm on cubic

data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/data/lifespan"
```

# QC ComBat Outputs

csvs scp'd from cubic

Log-Scaled

```{r}
imp.sites_log.cf_cf.gam <- fread(file=paste0(data_path, "/lifespan-CN-imp-sites_log-cf_cf.gam_data.csv"))
sum(is.na(imp.sites_log.cf_cf.gam))
sum(imp.sites_log.cf_cf.gam < 0)
skimr::skim(imp.sites_log.cf_cf.gam$lh_Vol_posteriorcingulate)
min(imp.sites_log.cf_cf.gam$lh_Vol_posteriorcingulate)
```

```{r}
imp.sites_log.cf_cf.gamlss <- fread(file=paste0(data_path, "/lifespan-CN-imp-sites_log-cf_cf.gamlss_data.csv"))
sum(is.na(imp.sites_log.cf_cf.gamlss))
skimr::skim(imp.sites_log.cf_cf.gam$log_age)
skimr::skim(imp.sites_log.cf_cf.gam$sex)
skimr::skim(imp.sites_log.cf_cf.gam$sex.age)
skimr::skim(imp.sites_log.cf_cf.gam$fs_version)
skimr::skim(imp.sites_log.cf_cf.gam$Vol_total)
```

```{r}
data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives"

pheno_list <- readRDS(file="cubic_scripts/R_scripts/pheno_list.rds")
vol_list_global <- readRDS(file="cubic_scripts/R_scripts/vol_list_global.rds")
vol_list_regions <- readRDS(file="cubic_scripts/R_scripts/Vol_list_regions.rds")
sa_list <- readRDS(file="cubic_scripts/R_scripts/SA_list.rds")
ct_list <- readRDS(file="cubic_scripts/R_scripts/CT_list.rds")

pheno_list.z <- paste0(pheno_list, ".z")
pheno_abs.diff.list <- paste0("abs.diff_", pheno_list)
z.pheno_abs.diff.list <- paste0("abs.diff_", pheno_list, ".z")

#also load raw data
ukb_cn_df <- fread("/Users/megardn/Desktop/BGD_Repos/combat_biovar/data/ukb_to_model/ukb_CN_data_simsites.csv")

#plotting info from dk atlas
dk.parc <- dk$data %>%
  as.data.frame() %>%
  na.omit() %>%
  dplyr::select(c(hemi, region, label)) %>%
  distinct()
```

>>>>

der_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/lifespan"

```

#Load

Combat-GAM Centiles

```{r}
gam_centile_df <- fread(file=paste0(der_path, "/cf.gam-batch.study_predictions.csv"))
```

Combat-LS Centiles

Deltas

```{r}

```
